### 2017-08-28 Documents/bootcamp_syllabus.tex
Updated Syllabus
Dates added to Syllabus

\subsubsection*{Where and When}
Meeting times: Monday and Wednesday 330-445pm\\

@@

@@

\textbf{Teaching Fellows}\\
\\
Felipe Alves 
Email: \href{mailto:mailto:falves@stern.nyu.edu}{falves@stern.nyu.edu}\\
Office hours: TBA\\

>>>>

\subsubsection*{Where and When}
Meeting times: Monday and Wednesday 330-445pm

@@

\subsection*{Important Dates}

Midterm Exam: \textbf{November 8, 2017}. Quick info: 75 minutes, in class, open book, open internet if the wireless is up, bring one page of notes. \\

\href{https://github.com/NYUDataBootcamp/Materials/blob/master/Documents/bootcamp_project.pdf}{Final Project} Due Date: End of day \textbf{December 21, 2017.}

@@

\textbf{Teaching Fellows}\\
\\
Felipe Alves \\
Email: \href{mailto:mailto:falves@stern.nyu.edu}{falves@stern.nyu.edu}\\
Office hours: TBA\\
